Ch3 process

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
I'm having issues with the estimation of parameters. I don't think this is right.

@@

```{r eval = FALSE, echo=TRUE}
###################################
# Run the experiments with different sample sizes and tail thresholds

@@

true.cdfs <- rep(0,num.qs)
for(i in 1:num.qs){

  iq <- q.tests[i]

  true.cdfs[i] <- sum(all.samples>iq)/length(all.samples)

all.true.cdfs <- rep(true.cdfs,num.ns)

sim.test.df <- data.frame(all.sampsizes=all.sampsizes, all.qtests=all.qtests,cdfs.hat=cdfs.hat,
                          true.cdfs = all.true.cdfs)
```

>>>>

lomax.st <- function(x=x, alpha=alpha, k=k){
  out <- alpha/(alpha+x)
  return(out^k)
}

lomax.mean <- function(alpha=alpha, k=k){
  return(alpha/(k+1))
}

@@

```{r}
# First estimate the mles for the different sample sizes

mles.sampsizes <- data.frame(samp.size = samp.sizes, alphas = 0, khats = 0)

for(i in 1:length(samp.sizes)){
  ith.n   <- mles.sampsizes$samp.size[i]
  ith.samples <- data.frame(x = sample(simplsamps$data, ith.n))

  # The glm.lomax was giving me an error. Kept saying it couldn't find the init betas but worked when I ran it line by line.

  # From the glm framework, we are not including covariates here
  # The next three lines are the arguments to the glm lomax function
  formula=~1
  my.dataf = ith.samples
  response = ith.samples$x

  # This is the glm lomax function deconstructed
  Y           <- response
  n           <- length(Y)
  designmat   <- model.matrix(formula, data=my.dataf)
  nbetas      <- ncol(designmat)
  init.betas  <- c(4,rep(5,nbetas))

  mles.sampsizes$alphas[i] <- alphas.hat
  mles.sampsizes$khats[i] <- k.hat
}

mles.sampsizes %>% 
  mutate(mean = lomax.mean(alphas, khats))

```
```{r}
# Now calculate the cdfs for each distribution and for each threshold

1-lomax.cdf(thresh.vals, alpha = mles.sampsizes$alphas[1], k = mles.sampsizes$khats[1])

```{r echo=TRUE}
###################################
# Run the experiments with different sample sizes and tail thresholds

all.samples <- simplsamps$data

@@
